### 2016-04-07 tips_and_notes/vim/chapter6/copyandpaste.tex
started on chapter 7

Copying and pasting text are essential features of any text editors.
I have already mentioned how to yank/change/delete/paste (\verb|y/c/d/p|) in vim, but there is a little bit more to it than just simply copy/deleting/pasting.

@@

>>>>

Copying and pasting text are essential features of any text editors.
I have already mentioned how to yank/change/delete/paste (\verb|y/c/d/p|) in vim, but there is a little bit more to it than just simply copy/deleting/pasting.
Just a quick note before we get started: \verb|gp/gP| does the same thing as the \verb|p/P| command, except that it leaves the cursor at the end of the pasted text.

@@

There are some registers in vim that are reserved for specific purposes:
\newline

\begin{tabular}{c|l}
    \verb|"%| & name of the current file you are editing\\
    \verb|"#| & name of the alternate file\\
    \verb|".| & last inserted text\\
    \verb|":| & last ex command\\
    \verb|"/| & last search pattern\\
\end{tabular}
\newline

\section{Visual selection and registers}

When you paste while in visual mode, the text which has been selected will be replaced with the text in the unnamed register.
This means that the selection that was overwritten by the paste is now in the unnamed register (i.e. the content of the unnamed register is swapped with the visual selection).
This can be useful if you want to rearrange words/lines/selection in your document.

\section{paste from register}

Sometimes it can be a little confusing whether to use \verb|p| or \verb|P|, as one will paste before and the other will paste after the cursor, respectively.
It may be helpful to go into Insert mode and use \verb|<ctrl-r>{register}|, as it will always paste the text after the cursor (as if we have typed it).
Also, together with \verb|c{motion}| (and others), you can make a useful dot command with it.
